### 2021-07-29 PrevAdjSurvey.tex

%\usepackage{algorithm}
%\usepackage{fancyhdr}
\usepackage{graphics,color,pict2e}
\usepackage{epsfig}
%\usepackage{times}
%\usepackage[cmbold]{mathtime}
%\usepackage{bm}
%\usepackage{rotating}
%\usepackage{pdflscape}
%\usepackage{longtable}
\usepackage{booktabs}

%\usepackage{C:/R/R-2.11.1/share/texmf/Sweave}

@@

>>>>

%\usepackage{algorithm}
%\usepackage{fancyhdr}
\usepackage{graphics,color,pict2e}
\usepackage{epsfig}
%\usepackage{times}
%\usepackage[cmbold]{mathtime}
%\usepackage{bm}
%\usepackage{rotating}
%\usepackage{pdflscape}
%\usepackage{longtable}
\usepackage{booktabs}
\usepackage{lscape}
\usepackage{pdflscape}    
%\usepackage{C:/R/R-2.11.1/share/texmf/Sweave}

@@

I present results for two scenarios:

\begin{itemize}
    \item The weight of each group is generated from a Dirichlet distribution with equal concentration parameters for all dimensions. The "Coefficient of Variation" in the figures referes to these weights.
    \item The true positivity of each group is generated from a Beta distribution which achieves the specified mean and ICC.
    \item Figure~\ref{fig:dws1}. Samples of 8,000 groups of 1. Population prevalence = 0.05\%/ Varying weight variance. Replicated 10,000 times.
    \begin{itemize}
        \item The two wsPoisson methods maintain appropriate or conservative coverage, regardless of the coefficient of variation among the weights.
        \item The other two methods (Agresti-Coull and Clopper-Pearson) only begin to falter at unrealistic or unusual (according to Barry) coefficients of variation.
        \item More typical coefficients of variation would be 20\%-40\%.
    \end{itemize}
    \item Figure~\ref{fig:dws2}. Samples of 200 groups of 50. Population prevalence = 0.05\%. Varying ICC. Varying weight variance. Replicated 10,000 times.
    \begin{itemize}
        \item Results here are a bit confusing.
        \item I know that the results for Agresti-Coull and Clopper-Pearson could be improved with a better estimate for \(\hat{\text{var}}(\hat{p}) \). The simple estimate I was using appears to perform poorly in the case of high ICC. \textbf{I wonder if Barry can point me towards a good estimator for \(\hat{\text{var}}(\hat{p}) \) in the presence of high ICC.}
        \item It is a bit strange that the wsPoisson methods perform better when there is extreme Coefficient of Variation, but it is consistent with the previously observed behavior of higher CoV leading to more conservative coverage.
    \end{itemize}
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/results_plot_8000_1.pdf}
    \caption{Dirichlet Weights Scenario 1}
    \label{fig:dws1}
\end{figure}

\pagebreak
\begin{landscape}
\begin{figure}
    \centering
    \includegraphics[width = \paperwidth]{figures/results_plot_200_50.pdf}
    \caption{Dirichlet Weights Scenario 2}
    \label{fig:dws2}
\end{figure}
\end{landscape}
\pagebreak

As you predicted, the usual methods (Agresti-Coull and Clopper-Pearson) exhibit poor performance when there is high variance among the weights.

Dean and Pagano recommend an adjustment suggested by Korn and Graubard that I wasn’t sure how to apply in the context of my simulation, so it’s possible that this is a pessimistic assessment of those methods.

Let’s chat about these results and next steps early next week.

Thanks,

Damon
